Add Code

### 2025-02-11 code.qmd
Tidy up the analysis code

report::report_sample(dat_clean, by = "sex", total = FALSE) |>
  knitr::kable()

```

@@

# Create ggplot object
ggplot2::ggplot(dat_clean, ggplot2::aes(x = sex, y = bill_length_mm, fill = sex), group = sex) +
  ggplot2::geom_violin(
    draw_quantiles = c(0.25, 0.5, 0.75),
    show.legend = FALSE
  ) +
  ggplot2::geom_jitter(width = 0.15, show.legend = FALSE) +
  ggplot2::labs(x = "Sex", y = "Bill length in mm") +
  ggplot2::theme_minimal()
```
``````

>>>>

report::report_sample(dat_clean, by = "sex", total = FALSE) |>
  knitr::kable()
```

@@

ggplot2::ggplot(dat_clean, ggplot2::aes(x = sex, y = bill_length_mm, fill = sex), group = sex) +
  ggplot2::geom_violin(
    draw_quantiles = c(0.25, 0.5, 0.75),
    show.legend = FALSE
  ) +
  ggplot2::geom_jitter(width = 0.15, show.legend = FALSE) +
  ggplot2::labs(x = "Sex", y = "Bill length in mm") +
  ggplot2::theme_minimal()
```
``````
